---
title: "Group_project"
author: "Anne, Aulia, Ilmul"
date: "2023-09-29"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Note : I turned off the code for cleaning process temporarily. 

### Library

``````{r, message=FALSE}
# opens library
library(haven)
library(dplyr)
library(tidyverse)
library(knitr)
library(kableExtra)
library(ggplot2)
library(broom.mixed)
library(parameters)
library(merDeriv)
library(sjPlot)
library(geepack)
library(readxl)
library(survey)
library(ggpubr)
library(gtsummary)
library(flextable)
library(labelled)

# function to count the missing values
count_missing_categorical <- function(column) {
  na_count <- sum(is.na(column))
  empty_count <- sum(column == "" | column == "NA" | column == "N/A") 
  
  if (is.na(na_count)) {
    return(empty_count)
  } else if (is.na(empty_count)) {
    return(na_count)
  }
  
  return(na_count + empty_count)
}
```

Bangladesh Adolescent Health And Wellbeing Survey (BAHWS) 2018-19

Size:

67093   Households completed

7800   Never Married Female adolescents 15-19  completed

### Open data set

```{r}
# load the codebook
#UF <- read.csv('~/SURVMETH687_group_pro/surv687-project/surv687-project/BAHWSd_UF.csv') #8284
```

The total observation is 8384. 

### Cleaning process

### 1. Check unit non response

```{r}
# only use the completed cases
#UF_completed <- UF[UF$QRESULT == 'Completed',] # n=7800
#dim(UF_completed)
```

There are 7800 Respondents completed the interviews. 

### 2. Check item non response

```{r}
# subset only for variable of interest
#UF_completed <- UF_completed[,c("recordID","QCLUSTER", "QNUMBER", "QLINE", "QHDIVISION", 
                                #"QHDISTRICT", "QHTYPE","QHQTYPE", "QRTYPE", "QINTNUM",  
                                #"QRESULT", "QWEIGHT_UF", # identity
                                #"UF104", "UF106", "UF107", "UF108", # Education level
                                #"UF109", # Jobs for the respondents
                                #"UF126E", # Affiliation with any club/organization
                                #"UF201",  # Technology access
                                #"UF206","UF207", # Internet usage behavior/Information                                                                            access
                                #"UF315A", "UF315B", "UF315C", "UF315D", # Internet usage behavior
                                                                        # Information access
                                #"UF702C", # Communication with mother
                                #"UF301", # "Did they experience menstruation?"
                                #"UF302", # Age first at menstruation
                                #"UF303", # Had knowledge about MP before experience
                                #"UF703A", # Talking with mother regarding menstruation
                                #"Domain", "Strata", "QHWLTHF", "QHWLTHI" # additional sampling information
                                #)]

#dim(UF_completed)
```

The total observation is 7800 with 34 variables. 

```{r}
# remove missing values in UF303 (the main variable of interest)
#UF_completed <- UF_completed[UF_completed$UF303!="",]
#dim(UF_completed) # n=3908
```

The total observation is 3908. 

```{r}
# check column names of the data
#colnames(UF_completed)
```


```{r}
# check the missing values for other variables
#summary_stats <- lapply(UF_completed[,c(13:30)], count_missing_categorical)
#column_summary <- sapply(summary_stats, function(x) x)
#print(column_summary) #there is still missing values for UF106, UF107, UF702C, UF703A
```

```{r}
# remove missing values in UF702C 
#UF_completed <- UF_completed[UF_completed$UF702C!="",]
#dim(UF_completed) # n=3820
```

The total observation is 3820. 

```{r}
# check the missing values 
#summary_stats <- lapply(UF_completed[,c(13:26)], count_missing_categorical)
#column_summary <- sapply(summary_stats, function(x) x)
#print(column_summary) #still have 17 missing values for variables UF106 and UF107
```

We still have missing values for UF106 and UF107.

```{r}
# remove missing values from UF107
#UF_completed <- UF_completed[UF_completed$UF107!="",]
#dim(UF_completed) #n=3803
```

The total observation is 3803. 

```{r}
# check the missing values 
#summary_stats <- lapply(UF_completed[,c(13:26)], count_missing_categorical)
#column_summary <- sapply(summary_stats, function(x) x)
#print(column_summary) #all complete cases
```

All variables are complete. No missing values. 

```{r}
# check dimension
#dim(UF_completed) #n=3803
```

The final observation is 3803 with 34 variables. 

```{r}
# check the distribution for each variables
#count_obervation <- function(column) {
#  obs_count <- table(column)
  
#  return(obs_count)
#}

#summary_stats <- lapply(UF_completed[,c(13:26)], count_obervation)
#column_summary <- sapply(summary_stats, function(x) x)
#print(column_summary)
```

There is no missing values anymore. The data is complete. 

### Save the data

```{r}
#write.csv(UF_completed, file="C:/Users/ASUS/Dropbox (University of Michigan)/Aulia Dini Rafsanjani’s files/GROUP_PROJECT_687/UF_clean2.csv", row.names = FALSE)
```

### Read data set

```{r}
# read data set
UF_clean2 <- read.csv("C:/Users/ASUS/Dropbox (University of Michigan)/Aulia Dini Rafsanjani’s files/GROUP_PROJECT_687/UF_clean2.csv")
```

### Descriptive Statistics

```{r}
var_label(UF_clean2) <- list(
                      QHTYPE = "Urban-rural status",
                      #UF104 = "Ever attended school",
                      #UF106 = "Highest class attended",
                      #UF107 = "Currently attending school",
                      #UF109 = "Currently working",
                      UF126E = "Affiliated with reading library",
                      #UF201 = "Have own mobile phone",
                      UF206 = "Use internet using computer",
                      UF207 = "Read any adolescent focused article",
                      #UF301 = "Experienced menstruation",
                      #UF302 = "Age of first menstruation",
                      UF303 = "Knowledge before experiencing menstruation",
                      UF315A = "Heard or watched anything about menstruation in TV/Radio",
                      UF315B = "Read anything about menstruation in Textbook/books",
                      UF315C = "Read anything about menstruation in Newspaper/magazine",
                      UF315D = "Read or watched anything about menstruation in the Internet",
                      #UF702C = "Talk with mother about very personal things",
                      UF703A = "Feel comfortable discussing about menstruation with mother")
```

```{r Sample characteristics, warning=FALSE, message=FALSE}
#Preparing table for initial descriptive statistics
set_gtsummary_theme(theme_gtsummary_compact(set_theme = TRUE))

#To get the descriptives
des1 <- UF_clean2 %>%
  dplyr::select(QHTYPE,UF126E,UF206,UF207,UF301,UF302,UF303,UF315A,UF315B,UF315C,UF315D,UF702C,UF703A) %>%
            tbl_summary(
              type = list(all_dichotomous() ~ "categorical",
                          all_continuous() ~ "continuous"),
              statistic = list(all_continuous() ~ "{mean} ({sd})",
                          all_categorical() ~ "{n} ({p}%)"),
              percent = "column",
              digits = all_continuous() ~ 1) %>%  
  bold_labels() %>% 
  italicize_levels() %>% 
  as_flex_table()

des1
```

### Create Multi-level Modelling using top-down approach

### Create full model with random effects (cluster)

```{r}
# change 303 to factor
UF_clean2$UF303 <- as.factor(UF_clean2$UF303)
UF_clean2$UF303 <- relevel(UF_clean2$UF303, ref = "No") 
```

```{r}
# change 206 as factor
UF_clean2$UF206 <- as.factor(UF_clean2$UF206)
UF_clean2$UF206 <- factor(UF_clean2$UF206, levels = c("Every day", "At least once a week", "Less than one a week", "Not at all"))
UF_clean2$UF206 <- relevel(UF_clean2$UF206, ref = "Not at all")
```

```{r}
# change QHTYPE as factor
UF_clean2$QHTYPE <- as.factor(UF_clean2$QHTYPE)
UF_clean2$QHTYPE <- factor(UF_clean2$QHTYPE, levels = c("Urban", "Other urban", "Rural"))
UF_clean2$QHTYPE <- relevel(UF_clean2$QHTYPE, ref = "Rural")
```

```{r}
#full model
fit.0 <- glmer(UF303 ~ factor(UF315A) + factor(UF315B) + factor(UF315C) + factor(UF315D) +  factor(UF126E) + factor(UF206) + factor(UF207) + factor(UF703A) + factor(QHTYPE) + (1 | QCLUSTER), 
             family = binomial, 
             nAGQ = 1, 
             data = UF_clean2)

summary(fit.0)
```

```{r}
# print the value of sigma 0 sq
sigma0_sq = fit.0@pp$theta ^ 2
sigma0_sq

# compute ICC
icc_0 = sigma0_sq / ( sigma0_sq + pi ^ 2 / 3 )
icc_0 
```

```{r}
# conduct lrt test to check the random effect
fit.0.null <- glm(UF303 ~ factor(UF315A) + factor(UF315B) + factor(UF315C) + factor(UF315D) +  factor(UF126E) + factor(UF206) + factor(UF207) + factor(UF703A) + factor(QHTYPE), 
             family = binomial, 
             data = UF_clean2)

summary(fit.0.null)
```

```{r}
# a function to compute p-value for lr test (lrt)
lrt.pvalue <- function(fit1, fit2) {
  lrtstat <-
    (-2 * as.numeric(logLik(fit2))) - (-2 * as.numeric(summary(fit1)$logLik))
  pvalue = 0.5 * (1 - pchisq(lrtstat, 2)) + 0.5 * (1 - pchisq(lrtstat, 1))
  return(pvalue)
}

lrt.pvalue(fit.0, fit.0.null) #significant for full model # continue to use random effect? # should we do lrt test for full model or reduced model?
```

### Create reduced model

```{r}
# reduced model
fit.a <- glmer(UF303 ~ factor(UF315A) + factor(UF315B) + factor(UF315D)  + factor(UF206)  + (1 | QCLUSTER), 
             family = binomial, 
             nAGQ = 1, 
             data = UF_clean2)

summary(fit.a)
```

```{r}
# print the value of sigma 0 sq
sigma0_sqa = fit.a@pp$theta ^ 2
sigma0_sqa

# compute ICC
icc_a = sigma0_sqa / ( sigma0_sqa + pi ^ 2 / 3 )
icc_a 
```

```{r}
# conduct lrt test to check the random effect
fit.a.null <- glm(UF303 ~ factor(UF315A) + factor(UF315B) + factor(UF315D)  + factor(UF206), 
             family = binomial, 
             data = UF_clean2)

summary(fit.a.null)
```

```{r}
lrt.pvalue(fit.a, fit.a.null) # random effect is significant for reduced model
```

### Compute AIC and BIC

```{r}
# compute AIC
AIC(fit.0)
AIC(fit.a)
```

```{r}
# compute BIC
BIC(fit.0)
BIC(fit.a)
```


# Model diagnostic

```{r}
# compute predicted probability
predicted_prob <- predict(fit.a, newdata = UF_clean2, type = "response")

# Combine predicted probabilities with the original dataset
result <- data.frame(UF303 = UF_clean2$UF303, Predicted_Prob = predicted_prob)

# Print the result
head(result)
```

```{r}
# create plot of predicted result 
ggplot(result, aes(x = UF303, y = Predicted_Prob)) +
  geom_boxplot(fill = "lightblue", color = "blue") +
  labs(x = "UF303 (Original Response)", y = "Predicted Probability") +
  ggtitle("Boxplot of Predicted Probability across UF303 Levels")
```


